Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-19 writeup/gz_hubble_data.tex
Doubled text leftover from merge
KLM comments on intro. Closes #129.

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12}
and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to
very large sample sizes, but do not always fully capture the relevant features,
especially for asymmetric galaxies that become increasingly common at high
redshifts. The Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual
classifications to measure galaxies in color-composite images. The efforts of
more than $2\times10^5$~classifiers allow for multiple independent
classifications of each image which are combined and calibrated to give a
distribution of vote fractions proportional to the probability of a feature
being visible. While crowdsourced data require extensive calibration
\citep{bam09,wil13}, they have a proven reliability and have been used for a
wide variety of scientific studies
\citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the classifications collected from the Galaxy Zoo Hubble
(GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third
phase of Galaxy Zoo, following its initial results classifying
$\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and
Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed
classification scheme that included bars, spiral arms, and galactic bulges
\citep{wil13}. GZH used a similarly detailed classification scheme, but focused
for the first time on images of high-redshift galaxies taken with \hst. The
Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model. This
evolution is a crude mechanism that mimics the brightness increase of galaxies
with increasing redshift (out to at least $z\sim1-2$). The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and increasing the effect to $e=-3.5$ in
increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows
several examples of the effects of ``losing'' spiral/disc features with
increasing redshift for two galaxies with $e=0$.

The final number of \ferengi{} images produced for each galaxy is ultimately a
function of galaxy's redshift (since the new images cannot be resampled at
better angular resolution than the original SDSS data), as well as the number
of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
images produced for GZH.

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the \ferengi{}
code to produce simulated \hst{} images. The measured value of \ffeatures{}
from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900,
0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875,
0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
\end{figure*}
>>>>>>> master

>>>>

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual classifications
to measure galaxies in color-composite images. The efforts of more than
$2\times10^5$~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the classifications collected from the Galaxy Zoo Hubble
(GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third
phase of Galaxy Zoo, following its initial results classifying
$\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and
Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed
classification scheme that included bars, spiral arms, and galactic bulges
\citep{wil13}. GZH used a similarly detailed classification scheme, but focused
for the first time on images of high-redshift galaxies taken with \hst. The
Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
high redshift, but using ACS and WFC3 rest-frame infrared imaging (Simmons
et~al., submitted).

@@
